New strategies for improving kidney exchange

### 2018-02-11 ec-18/kidney-ec-submission.tex
Pseudo-reward intuition figure

\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

@@

\begin{figure}[H]
\centering
\hspace*{-3.5cm}
\includegraphics[width=1.4\textwidth]{/Users/vitorhadad/Documents/kidney/matching/phd_thesis/figures/greedy_opt_comparison_mcl2_2.pdf}
\caption{Ratio of \texttt{Myopic} has better chances of achieving performances similar to \texttt{OPT} when the death rate is high (moving rightwards on the graphs), or when entry rate is high (moving downwards on the graphs).}
\label{fig:greedy_opt_compariso}
\end{figure}

@@

\begin{figure}[H]
\centering
\hspace*{-1cm}
\includegraphics[width=1.1\textwidth]{/Users/vitorhadad/Documents/kidney/matching/phd_thesis/figures/direct_prediction.pdf}.
\caption{Direct prediction methods.}
\label{fig:direct_prediction}
\end{figure}

@@

 \begin{figure}
  \centering
  \hspace*{-1cm}
  \includegraphics[width=1.1\textwidth]{/Users/vitorhadad/Documents/kidney/matching/phd_thesis/figures/mab.pdf}
  \caption{\textbf{Function} \textsc{choose\_cycle}}
  \label{fig:mab}
  \end{figure}

  \begin{figure}
  \centering
  \includegraphics[width=1.1\textwidth]{/Users/vitorhadad/Documents/kidney/matching/phd_thesis/figures/mab_step.pdf}
  \caption{\textbf{Function} \textsc{get\_pseudo\_reward} }
  \label{fig:get_pseudo_reward}
  \end{figure}

@@

\newcommand\mycommfont[1]{\footnotesize\upshape\textcolor{blue}{#1}}
\SetCommentSty{mycommfont}

% Algorithm
\begin{algorithm}[t]
	\SetAlgoLined
	\KwData{Cycle $c$; Horizon $h$; \\
          Lists pseudo-reward statistics $Avg$, $Std$; \\
          Environment simulator object \textsc{Env}; \\
          Oracle solver \textsc{OPT}; }
  \DontPrintSemicolon
  \SetKwFunction{FChoose}{\textsc{get\_pseudo\_reward}}
  \SetKwProg{Fn}{Function}{:}{}
  \Fn{\FChoose{\textsc{Env}, \ $c$, \ $Avg$, \ $Std$, \ $h$ }}{
    \tcp{Simulate up to horizon $h$ and find optimal matching} \\
    \textsc{Env.simulate}($h$)  \\
    $r_1$ \gets \textsc{OPT.solve}(\textsc{Env})  \\
    \tcp{Remove cycle $c$, find constrained optimal matching} \\
    \textsc{Env.remove}($c$)  \\
    $r_2$ \gets \textsc{OPT.solve}(\textsc{Env}) \\
    \tcp{Return 1 if rewards are equal, 0 otherwise} \\
    \KwRet $r_1 == r_2$ \;
  }
	\caption{Function \textsc{get\_pseudo\_reward}}
	\label{alg:get_pseudo_reward}
\end{algorithm}

\begin{algorithm}[t]

>>>>

\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}
\newcommand\mycommfont[1]{\footnotesize\upshape\textcolor{blue}{#1}}
\SetCommentSty{mycommfont}

@@

\begin{figure}[H]
\centering
\hspace*{-3.5cm}
\includegraphics[width=1.4\textwidth]{/Users/vitorhadad/Documents/kidney/matching/phd_thesis/figures/greedy_opt_comparison_mcl2_2.pdf}
\caption{Ratio of \texttt{Myopic} has better chances of achieving performances similar to \texttt{OPT} when the death rate is high (moving rightwards on the graphs), or when entry rate is high (moving downwards on the graphs).}
\label{fig:greedy_opt_comparison}
\end{figure}

\begin{algorithm}[htbp]
	\SetAlgoLined
  \DontPrintSemicolon

  \KwData{Environment simulator object \textsc{Env}; \\
          Integer programming solver object \textsc{Solver}; \\
          Statistical method \textsc{Classifier} \\
          Threshold $thres$; }

  \SetKwFunction{FChoose}{\textsc{direct\_prediction}}
  \SetKwProg{Fn}{Function}{:}{}
  \Fn{\FChoose{\textsc{Env}, \ \textsc{Solver}, \ \textsc{Classifier}, \ $thres$}}{
    \tcp{Retrieve data about nodes and (potentially) graph from current environment} \\
    $X, E_1, E_2$ \gets \textsc{Env.get\_data}()  \\
    \tcp{Pass data through classifier, predict matching probability for each pair} \\
    $prob$ \gets \textsc{Classifier}($X$, \ $E_1$, $E_2$)  \\
    \tcp{Get index of pairs whose probability is higher than threshold} \\
    $index$ $\gets$ \textsc{which}($prob > thres$) \\
    \tcp{Find maximal matching restricted to this subset} \\
    chosen\_cycles $\gets$ \textsc{Solver.solve(Env, subset=$index$)}  \\  
    \tcp{Return chosen cycles to be cleared} \\
    \KwRet chosen\_cycles \;
  }
	\caption{Function \textsc{direct\_prediction}}
	\label{alg:direct_prediction}
\end{algorithm}

@@

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{/Users/vitorhadad/Documents/kidney/matching/phd_thesis/figures/direct_prediction.pdf}.
\caption{One period of simulation using direct prediction methods to choose cycles.}
\label{fig:direct_prediction}
\end{figure}

@@

 \begin{figure}
  \centering
  %\hspace{-1cm}
  \includegraphics[width=1\textwidth]{/Users/vitorhadad/Documents/kidney/matching/phd_thesis/figures/mab.pdf}
  \caption{One period of simulation using multi-armed bandit methods to choose cycles.}
  \label{fig:mab}
  \end{figure}

  \begin{figure}
  \centering
  %\hspace*{-0.5cm}
  \includegraphics[width=1\textwidth]{/Users/vitorhadad/Documents/kidney/matching/phd_thesis/figures/mab_step.pdf}
  \caption{\textbf{Function} \textsc{get\_pseudo\_reward} \\ Multi-armed bandits evaluate if a cycle should be cleared by checking if there is a high chance that the cycle will be used in the future. Such cycles get a \emph{lower} reward, and are left for later.}
  \label{fig:get_pseudo_reward}
  \end{figure}

\paragraph{What are pseudo-rewards?} Figure \ref{fig:pseudo_reward_intuition}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.95\textwidth]{/Users/vitorhadad/Documents/kidney/matching/phd_thesis/figures/pseudo_reward_intuition.pdf}
\caption{Pseudo-reward intuition}
\label{fig:pseudo_reward_intuition}
\end{figure}

@@

% Algorithm
\begin{algorithm}[htbp]
	\SetAlgoLined
	\KwData{Cycle $c$; Horizon $h$; \\
          Lists pseudo-reward statistics $Avg$, $Std$; \\
          Environment simulator object \textsc{Env}; \\
          Oracle solver \textsc{OPT}; }
  \DontPrintSemicolon
  \SetKwFunction{FChoose}{\textsc{get\_pseudo\_reward}}
  \SetKwProg{Fn}{Function}{:}{}
  \Fn{\FChoose{\textsc{Env}, \ $c$, \ $Avg$, \ $Std$, \ $h$ }}{
    \tcp{Simulate up to horizon $h$ and find optimal matching} \\
    \textsc{Env.simulate}($h$)  \\
    $r_1$ \gets \textsc{OPT.solve}(\textsc{Env})  \\
    \tcp{Remove cycle $c$, find constrained optimal matching} \\
    \textsc{Env.remove}($c$)  \\
    $r_2$ \gets \textsc{OPT.solve}(\textsc{Env}) \\
    \tcp{Return 1 if rewards are equal, 0 otherwise} \\
    \KwRet $r_1 == r_2$ \;
  }
	\caption{Function \textsc{get\_pseudo\_reward}}
	\label{alg:get_pseudo_reward}
\end{algorithm}

\begin{algorithm}[htbp]
